\documentclass[12pt]{article}
\usepackage{amsgen,amsmath,amstext,amsbsy,amsopn,amssymb}
%\usepackage[dvips]{graphicx,color}
\usepackage{graphicx,color}
\usepackage{graphicx,color,bm}
\usepackage{epsfig}
\usepackage{enumerate}
\usepackage{float}
\usepackage{multicol}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{wrapfig,lipsum,booktabs}
%\setlength{\oddsidemargin}{0.1 in} \setlength{\evensidemargin}{-0.1
%in} \setlength{\topmargin}{-0.6 in} \setlength{\textwidth}{6.5 in}
%\setlength{\textheight}{8.5 in} \setlength{\headsep}{0.75 in}
%\setlength{\parindent}{0 in} \setlength{\parskip}{0.1 in}

\textwidth 6.3in \textheight 8.8in \topmargin -0.5truein
\oddsidemargin .15truein
\parskip .1in
\renewcommand{\baselinestretch}{1.00}  % double spaced
\renewcommand{\thesection}{\Roman{section}} 
\renewcommand{\thesubsection}{\thesection.\Roman{subsection}}
\usepackage{caption}

\begin{document}
	
	\title{%
		HW1: MNIST Exploration}
	\author{\bf Alexander Van Roijen}
	
	\maketitle
	\section{Introduction and Overview}
	
	\section{Theoretical Background}
	
	\section{Algorithm Implementation and Development}

	
	\section[Look what i made]{Computational Results}

	\section[see]{Summary and Conclusions}

	\section{Future Work}

	\section{References}
	\begin{itemize}
		\item 1: Seattle Animal Shelter. Seattle Pet Licenses. Seattle, WA: Department of Finance and Administrative Services, February 28, 2019. Electronic. February 2019. https://data.seattle.gov/Community/Seattle-Pet-Licenses/jguv-t9rb
		\item 2: United States Census Bureau / American FactFinder. “ 2013-2017 American Community Survey 5-Year Estimates” 2015-2018 American Community Survey. U.S. Census Bureau’s American Community Survey Office, 2017. Web. 1 March 2019 <http://factfinder2.census.gov>.
		\item 3: Di Donfrancesco, Brizio et al. “Consumer Acceptance of Dry Dog Food Variations.” Animals 4.2 (2014): 313–330. Crossref. Web.
		\item 4: “How Much Does a Cat Cost?” Petfinder, 21 Sept. 2017, www.petfinder.com/pet-adoption/cat-adoption/how-much-does-a-cat-cost/.
		\item 5:
		“How Much Does a Dog Cost?” Petfinder, 21 Sept. 2017, www.petfinder.com/pet-adoption/dog-adoption/how-much-does-a-dog-cost/.
		
	\end{itemize}
	\section{Appendix A}

	\section{Appendix B}

	\subsection{Approach}

	\begin{wraptable}{l}{0.7\linewidth}
		\centering
		\begin{tabular}{|c||c||c||c||c|c|}
			\hline
			count & ... & Cat & M.H.I & zip & year \\
			100 & ... & 1 & 58000 & 98107 & 2017 \\
			200 & ... & 0 & 58000 & 98107 & 2017 \\
			\hline
		\end{tabular}
	\end{wraptable}

	%\subsection[Data Plumbing]{Data Plumbing}



\end{document}